%==============================================================
% Jayash Bhandary — Resume (one page, mirrors the web viewer)
% Compile with: tectonic resume.tex   (or pdflatex resume.tex)
% Uses only standard packages (article class) — no exotic deps.
%==============================================================
\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.4cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{accent}{HTML}{2F5BFF}
\definecolor{soft}{HTML}{5A6068}
\definecolor{faint}{HTML}{9AA0A8}

\hypersetup{
    colorlinks=true,
    urlcolor=accent,
    linkcolor=accent,
    pdftitle={Jayash Bhandary — Resume},
    pdfauthor={Jayash Bhandary},
    pdfsubject={Full-Stack \& AI Engineer},
    pdfkeywords={Full-Stack Engineer, AI Engineer, React, Next.js, FastAPI, RAG, LLM, Python}
}

% Section headings — uppercase accent label with a rule
\titleformat{\section}
    {\small\bfseries\color{accent}}
    {}{0em}{\MakeUppercase}[\vspace{1pt}{\color{faint}\titlerule}]
\titlespacing{\section}{0pt}{8pt}{4pt}

\setlist[itemize]{leftmargin=1.1em, itemsep=0pt, topsep=1pt, parsep=0pt}
\pagestyle{empty}
\setlength{\parindent}{0pt}

% Experience entry: {role — org}{type • dates}
\newcommand{\entry}[2]{%
    \textbf{#1}\hfill{\small\color{faint}\textit{#2}}\par%
}

\begin{document}

%---------------- Header ----------------
\begin{center}
    {\Huge\bfseries Jayash Bhandary}\\[3pt]
    {\color{soft}Full-Stack \& AI Engineer \textbullet{} Bengaluru, India}\\[5pt]
    {\small
    \href{mailto:findjayash@gmail.com}{findjayash@gmail.com} \textbullet{}
    \href{tel:+919136007794}{+91 91360 07794} \textbullet{}
    \href{https://jayashbhandary.github.io}{Portfolio} \textbullet{}
    \href{https://github.com/JayashBhandary}{GitHub} \textbullet{}
    \href{https://www.linkedin.com/in/jayashbhandary}{LinkedIn}}
\end{center}
\vspace{-2pt}
{\color{soft}\hrule height 1.2pt}
\vspace{2pt}

%---------------- Summary ----------------
\section*{Summary}
Computer Science graduate with hands-on experience building full-stack web applications and
AI-driven systems. Worked on real projects involving React, Next.js, Node.js, FastAPI, and cloud
deployments, along with LLM-based features like RAG pipelines and multi-model integrations.
Comfortable taking features from idea to production, focused on clean, practical code that solves
real problems.

%---------------- Experience ----------------
\section*{Work Experience}

\entry{AI Engineer --- Syneca}{On-site \textbullet{} Aug 2025 -- Present}
\begin{itemize}
    \item Worked on SYNECA, a smart archival system for data.
    \item Implemented multi-LLM provider and vector DB support for the SIA agent.
    \item Built an MCP server for SYNECA so it can be accessed by any chatbot or LLM.
\end{itemize}
\vspace{4pt}

\entry{Frontend Developer --- ZOOMBUY}{Freelance \textbullet{} Jan 2025 -- Jun 2025}
\begin{itemize}
    \item Developed an SEO-optimized e-commerce website using Shopify as the backend platform.
    \item Implemented a responsive UI with performance-optimized components.
    \item Reduced bounce rate through better UX and faster load times.
\end{itemize}
\vspace{4pt}

\entry{Full-Stack Developer --- 2WENT6EX}{Freelance \textbullet{} Dec 2023 -- Jul 2024}
\begin{itemize}
    \item Built a non-contemporary fashion website from scratch using modern web technologies.
    \item Led the complete lifecycle: planning, design, development, testing, and deployment.
    \item Ensured high responsiveness and cross-device compatibility, improving client satisfaction.
\end{itemize}

%---------------- Two columns: Education + Skills ----------------
\vspace{2pt}
\noindent
\begin{minipage}[t]{0.40\textwidth}
    \section*{Education}
    \textbf{B.Sc. Computer Science}\hfill{\small\color{faint}2022--2025}\\
    {\color{soft}\small V.P.M's R. Z. Shah College, Mulund}\\[3pt]
    \textbf{Higher Secondary (HSC)}\hfill{\small\color{faint}2020--2022}\\
    {\color{soft}\small VPM Junior College, Mulund}\\[3pt]
    \textbf{Secondary (SSC)}\hfill{\small\color{faint}2010--2020}\\
    {\color{soft}\small Little Flower High School, Thane}
\end{minipage}\hfill
\begin{minipage}[t]{0.56\textwidth}
    \section*{Skills}
    \textbf{Languages:} JavaScript, TypeScript, Python, C++, C\#, Dart, SQL\\
    \textbf{Frontend:} React.js, Next.js, Tailwind CSS, Framer Motion, Vite\\
    \textbf{Backend:} Node.js, FastAPI, Express.js, Serverless\\
    \textbf{AI / ML:} PyTorch, Hugging Face, OpenAI API, Gemini, LangChain, RAG\\
    \textbf{Cloud \& DevOps:} AWS, GCP, Docker, GitHub Actions, CI/CD, Terraform\\
    \textbf{Databases:} PostgreSQL, MongoDB, Redis, ChromaDB
\end{minipage}

%---------------- Certifications ----------------
\section*{Certifications}
Vertex AI Gemini API \textbullet{} GenAI Apps with Gemini \& Streamlit \textbullet{} Google Cloud Essentials
\textbullet{} Prompt Design in Vertex AI \textbullet{} Gemini Multimodality \& Multimodal RAG \textbullet{}
Neo4j Certified Professional \textbullet{} AI Apps with Gemini \& Imagen \textbullet{} SQL to MongoDB
Document Model \textbullet{} MongoDB Schema Design Patterns \textbullet{} RAG Course for Beginners

\end{document}
